---
title: "R Notebook"
output:
  html_document:
    df_print: paged
editor_options: 
  markdown: 
    wrap: 72
---

# 

Univariate and Bivariate Analysis

### Team/Group Introduction - Group 11 - Section 01

Vidya Biradar & Sujata Biswas

## *Academic Integrity -*

*We, Vidya, and Sujata, hereby state that we have not communicated with
or gained information in any way from any person or resource that would
violate the College's academic integrity policies, and that all work
presented is our own. In addition, we also agree not to share our work
in any way, before or after submission, that would violate the College's
academic integrity policies.*

-   Versions of R and Rstudio R Version:

```{r}
print(R.version.string)
```

Rstudio Version RStudio 2022.12.0+353 "Elsbeth Geranium" Release
(7d165dcfc1b6d300eb247738db2c7076234f6ef0, 2022-12-03) for Windows

Mozilla/5.0 (Windows NT 10.0; Win64; x64) AppleWebKit/537.36 (KHTML,
like Gecko) RStudio/2022.12.0+353 Chrome/102.0.5005.167 Electron/19.1.3
Safari/537.36

-   Packages used in the project:

1.  install.packages("ggplot")

2.  install.packages("plotly")

3.  install.packages("dplyr")

4.  install.packages("hexbin")

```{r}
#importing a ggplot2 library
library(ggplot2)
library(plotly)
library(dplyr)
library("hexbin")
```

Load the Dataset from csv file

```{r}
#reading a csv file from excel
amazon<-read.csv("C:/Users/sujat/OneDrive/Documents/DAB 501/a2.csv")
```

-   Dataset Documentation:

This dataset contains the data of 1K+ Amazon Product's Ratings and
Reviews as per their details listed on the official website of Amazon

-   Variables/Features:

    | VARIABLE            | MEANING                                                       |
    |---------------------|---------------------------------------------------------------|
    | product_id          | Product ID                                                    |
    | product_name        | Name of the Product                                           |
    | category            | Category to Which the Product Belongs                         |
    | discounted_price    | Discounted Price of the Product                               |
    | actual_price        | Actual Price of the Product                                   |
    | discount_percentage | Percentage of Discount on the Product                         |
    | rating              | Rating of the Product                                         |
    | rating_count        | Number of people who rated for the Amazon rating of a Product |
    | about_product       | Description about the Product                                 |
    | user_id             | ID of the user who wrote review for the Product               |
    | user_name           | Name of the user who wrote review for the Product             |
    | review_id           | ID of the Review given by the User                            |
    | review_title        | Brief Review                                                  |
    | review_content      | Detailed Review                                               |
    | img_link            | Image Link of the Product                                     |
    | product_link        | Official Website Link of the Product                          |

-   Data Processing

```{r}
#Data preprocesing
amazon$discounted_price <- gsub("[^0-9]", "", amazon$discounted_price)
amazon$actual_price <- gsub("[^0-9]", "", amazon$actual_price)
amazon$rating_count <- gsub("[^0-9]", "", amazon$rating_count)
amazon$discount_percentage <- gsub("[^0-9]", "", amazon$discount_percentage)
```

The dataset contains columns which are supposed to have only numeric
values but these contain characters other than numbers, thus, we needed
to remove these for further processing and analysis. We used gsub
function to remove prefix and suffix non-numeric values from these
columns.

Further, as and when necessary, we have converted a few columns into
numerical type and also have added categorical type of column(s) based
on other column(s). (*Explanation is provided whenever and wherever data
is processed.*)

# Plots \| ggplot

## UNIVARIATE ANALYSIS:

### 1. Numerical Variable:

#### a. Visualization of the 'main_category' Variable-

##### Distribution of Counts

As there are lot of categories we needed to categorize them into main
categories. To achieve this we have used =LEFT(C2, FIND("\|", C2,
FIND("\|", C2)+1)-1) formula to create a new column called main_category
which is used to visualize the sales data in each category.

```{r}
#plot 1
# visualization of the distribution of counts
ggplot(data = amazon) +
  geom_bar(mapping = aes(x = main_category), fill = "thistle3", color = "black") +
  labs(x = "",y = "",
  title = "PRODUCT CATEGORIES") +
theme(axis.text.x = element_text(angle = 45,
                                 hjust = 1,
                                 color = "mediumpurple4"),
  axis.text.y = element_text(color = "mediumpurple4"),
  plot.title = element_text(face = "bold",
                            hjust = 0.5,
                            color = "mediumpurple4"),
  legend.text = element_text(color = "mediumpurple4"),
  panel.grid.major = element_line(color = "seashell2"),
  panel.background = element_rect(fill = "white"))
```

Visualization (Plot 1 ) is a bar plot that displays the total count of
the products sold in each category with the y-axis showing the range of
data from 0 to 500 and x-axis as a main category.

##### Distribution of Proportions

```{r}
# visualization of the distribution of proportions
prop_table <-amazon %>% count(main_category) %>%   mutate(props = n / sum(n))
ggplot(prop_table) +
  geom_bar(aes(x = "", y = props, fill = main_category),width = 1,stat = "identity") +
  coord_polar("y", start = 0) +
  labs(x = "",y = "",
  title = "PROPORTIONS OF EACH PRODUCT CATEGORY") +
theme(plot.title = element_text(face  = "bold",hjust = -0.1,color = "darkslategrey"),
  panel.grid = element_blank(),
  panel.background = element_rect(fill = "white"),
  legend.text = element_text(color = "darkslategrey"),
  legend.position = "right",
  legend.title = element_blank()) +
  guides(fill = guide_legend(title = "main category")) +
  scale_fill_discrete(labels = paste(prop_table$main_category,
  scales::percent(prop_table$props),sep = " - ")) + 
  scale_fill_brewer(palette = "Set3") 

```

The above visualization in a pie chart gives us a clear idea about the
distribution of proportions of each sub-category in the main category
column.

##### Analysis-

-   [Unusual Observations-]{.underline} From the plot created we can
    observe that the 'Electronics' and 'Home & Kitchen' categories have
    the highest number of products, while the 'Others' category has the
    lowest number of products. This suggests that the dataset may be
    skewed towards these two categories, and there may not be enough
    representation of products from other categories.

-   [Unique Values-]{.underline} We can see that there are far too few
    values in some of the sub-categories namely 'Car & Motorbike',
    'Electronics', 'Home Improvement', 'Musical Instruments' and lastly
    'Toys & Games'.

#### b. Visualization of the 'status' Variable-

##### Distribution of Counts

```{r}
amazon$net <- as.numeric(amazon$rating)
amazon$net[is.na(amazon$net)] <- 0
amazon$status <- ifelse(amazon$net >=4, "excellent", ifelse(amazon$net <=3, "bad", "good"))
```

Herein, we have created a categorical variable 'status' based on ratings
of the products which required us to first turn the 'rating' column into
a numerical one from categorical where we were also required to fill in
any missing values with 0. We have the named this variable as 'net'. The
'status' categorical column specifies if the product has been rated 4 or
above as 'excellent', 3 or below as 'bad' and anything apart from that
(between 3 and 4) as 'good'.

```{r}
#plot 2
#Review of each category
ggplot(data = amazon) +
  geom_bar(mapping = aes(x = status, 
                         fill = main_category)) +
  scale_fill_brewer(palette = "Pastel1") +
  coord_flip() + 
  labs(x = "",y = "",
  title = "REVIEW OF EACH CATEGORY") +
theme(axis.text.x = element_text(
                                 hjust = 1,
                                 color = "slateblue1"),
  axis.text.y = element_text(color = "slateblue1"),
  plot.title = element_text(face = "bold",
                            hjust = 0.5,
                            color = "slateblue4"),
  legend.text = element_text(color = "slateblue4"),
  panel.grid.major = element_line(color = "seashell2"),
  panel.background = element_rect(fill = "white"))
```

##### Distribution of Proportions

```{r}
ggplot(amazon,aes(x = status,fill = main_category)) + 
    geom_bar(position = "fill") +
  scale_fill_brewer(palette = "GnBu") + 
  # Set color scheme for legend
  labs(title = "MAIN CATEGORIES DISTRIBUTED BY THEIR STATUS", x = "Status", y = "Count") +
  theme(plot.title = element_text(face = "bold",
                            hjust = 0.5,
                            color = "hotpink4"),
    # Customize legend title
    legend.title = element_text(size = 14, 
                                face = "bold", 
                                color = "hotpink4"), 
        # Customize legend text
        legend.text = element_text(color = "hotpink4"), 
        # Customize axis titles
        axis.title = element_text(size = 14, 
                                  face = "bold", 
                                  color = "hotpink4"), 
        # Customize axis labels
        axis.text = element_text(size = 12, 
                                 color = "hotpink4"),
  panel.background = element_rect(fill = "white")) 

```

#### Analysis-

The bar graph plotted gives us a clear count of each review of the
product categories meaning that how many ratings each product category
has received as bad, good or excellent. The next bar graph for
proportions shows how much proportion of the ratings belong to each
category of product.

-   [Unusual observations-]{.underline} There are no unusual
    observations as such as it is a graph plotted over the ratings given
    by the people and each person's opinion is subjective.

-   [Unique Values-]{.underline} One noticeable feature is that
    'Computers&Accessories', 'Electronics' and 'Home&Kitchen'
    sub-categories of products have received the most number of ratings
    be it bad, good or excellent, as compared to the other
    sub-categories.

### 2. Numerical Variable:

#### a. Visualization for 'rating' Variable-

```{r}
ggplot(amazon, aes(x=rating, fill= main_category))+
geom_bar() + 
   scale_fill_brewer(palette = "RdPu") + 
  labs(x="Rating", y="", title="RATING OF PRODUCTS") + 
  theme(panel.background = element_rect(fill = "white"),
        plot.title = element_text(face = "bold",
                            hjust = 0.5,
                            color = "purple4"),
         axis.title = element_text(size = 16, 
                                  face="bold",
                                  color = "purple4"),
         axis.text = element_text(color = "purple4"),
        legend.title = element_text(size = 14, 
                                    color = "purple4", 
                                    face="bold"),
        legend.text = element_text(color = "purple4"))
```

```{r}
#plot 3
#boxplot of rating to check for outliers
#converting rating as numeric
rate<- as.numeric( amazon$rating)
#replacing missing value as 0
rate<-replace(rate,is.na(rate),0)
table(is.na(rate))
ggplot(amazon, aes(y=rate)) +
  geom_boxplot(fill="lightblue", color="dodgerblue4", alpha=0.5) +
  labs(x="", y="Rating", title="RATING OF PRODUCTS") +
  scale_x_discrete(labels=c("Rating")) +
  theme_minimal(base_size = 16) +
  theme(plot.title = element_text(face = "bold",
                            hjust = 0.5,
                            color = "dodgerblue4"),
        axis.line = element_line(size = 1,
                                 color = "white"),
        axis.text = element_text(color = "steelblue3"),
        axis.title = element_text(size = 16, 
                                  color = "dodgerblue4",
                                  face="bold")) 
```

##### Analysis-

Here, we have created a bar plot and boxplot of the number of ratings
recorded. The different colors in each bar gives us the idea of what
ratings belong to which sub category of products.

-   Identifying Outliers- The outliers can be clearly identified just by
    observing the two plotted graphs above. Any data point lying at an
    abnormal distance from the rest of the data points is regarded as an
    outlier. They can also be identified using Inter Quartile Range(IQR)
    method and finding out the different quartiles and IQR along with
    them (done in further steps).

-   Shape of the Data- By Observing the graph plotted above, we can see
    that the data for rating is negatively skewed.

-   Transformation- The data being skewed needs to be transformed for
    better visualization and analysis. The accuracy of analysis can be
    compromised by outliers, which can distort analysis. The accuracy of
    the analysis can be improved, and more informative results can be
    produced by removing outliers. Thus we need to apply transformation
    to normalize the data.

    The outliers can be identified and removed by applying IQR method.
    Any data point lying outside the range of (q1 - 1.5\*iqr_x , q3 +
    1.5\*iqr_x) is regarded as an outlier and thus these have been dealt
    with.

```{r}
# removing outliers using iqr method
amazon$net <- as.numeric(amazon$rating)
amazon$net[is.na(amazon$net)] <- 0
q1 <- quantile(amazon$net, 0.25)
q3 <- quantile(amazon$net, 0.75)
iqr_x <- IQR(amazon$net)

data1 <- amazon[(amazon$net >= q1 - 1.5*iqr_x) & (amazon$net <= q3 + 1.5*iqr_x), ]

```

#### Visualization for 'rating' Variable after removing Outliers-

```{r}
#boxplot without outliers
ggplot(data1, aes(y = net)) +
  geom_boxplot(fill = "#f2c595", color = "black") +
  labs(x = "", y = "Rating", title = "RATING OF PRODUCTS") +
  theme_minimal(base_size = 16) +
  theme(plot.title = element_text(face = "bold",
                            hjust = 0.5),
        axis.title = element_text(size = 16, 
                                  face="bold"))
  
```

##### Analysis-

The data appears to be asymmetrical as it is left-skewed.

-   Measure of Central Tendency- Median

```{r}
median(amazon$net)
```

-   Explanation for Median- The first box plot and bar plot suggests
    that the data are left-skewed, therefore **Median** might be a more
    accurate measure of central tendency than the mean as extreme values
    have less of an impact on the median.

-   Measure of Spread- It is crucial to employ an outlier-resistant
    spread measure. The interquartile range (IQR) is a dependable spread
    indicator that is less susceptible to outliers than the standard
    deviation (IQR). The box plot made later shows the quartiles, and
    median of the data.

```{r}
IQR(amazon$net)
```

-   Explanation for Choosing IQR- Inter Quartile Range(IQR) is measure
    of where the majority of the values are. It can be used as a measure
    of variability if the extreme values are not being recorded
    precisely. Another important feature of IQR is that extreme values
    have no impact on it; meaning that it is not affected by outliers.

#### b. Visualization for 'discount_percentage' Variable

Before we plot the graph for 'discount_percentage', we will check the
type of data and remove any non-numeric character entries from the
column and also convert it into numerical type just to make sure.

```{r}
# Check the data type and range of the variable you're trying to log transform
class(amazon$discount_percentage)
range(amazon$discount_percentage)

# Convert the variable to numeric if it's a factor or character
amazon$discount_percentage <- as.numeric(as.character(amazon$discount_percentage))

# Adjust the range of the data or use a different transformation if the variable contains negative values
amazon$discount_percentage <- amazon$discount_percentage + abs(min(amazon$discount_percentage)) + 1
```

```{r}
#displaying the content of the list
str(amazon$actual_price)
str(amazon$discount_price)
```

```{r}
#converting both actual price and discounted price as numeric
amazon$actual_price <- as.numeric(amazon$actual_price)
amazon$discounted_price <- as.numeric(amazon$discounted_price)
```

```{r}
#plot 4
#histogram displaying discount percentage and its count
ggplot(amazon, aes(x = discount_percentage)) +
  geom_histogram(alpha = 0.7, 
                 bins = 30, 
                 fill = "seashell2", 
                 color = "wheat4") +
  labs(x = "Percentage of Discount", 
       y = "Count", 
       title = "BEHAVIOR OF DISCOUNT PERCENTAGE OF PRODUCTS") +
  theme_minimal() +
  theme(plot.title = element_text(face = "bold",
                            hjust = 0.5,
                            color = "wheat4"),
        axis.line = element_line(size = 1,
                                 color = "wheat4"),
        axis.title = element_text(size = 16, 
                                  face = "bold",
                                  color = "wheat4"))

```

##### Analysis-

-   Identifying Outliers- By observing the histogram plotted for the
    'discount_percentage' variable, we can clearly say that this data
    does not include any outliers there are no such observations at an
    abnormal distance from the majority of the others. Also, the graph
    being of 'discount_percentage' itself means that it would not
    contain any outliers as the discount percentages are bound to vary
    product to product.

-   Shape of the Data- The data is symmetrical as it follows normal
    distribution and there are no such outliers present.

-   As the data is already symmetrical, we need not apply any
    transformation methods to the data. Transformation of data is
    required only when the data is asymmetrical or has any outliers
    present.

-   Measure of Central Tendency- Mean

```{r}
mean(amazon$discount_percentage)
```

-   Explanation for Mean- To calculate the central tendency of this data
    we can consider its mean as it would not be hindered due to any
    outliers as the data is symmetrical and not skewed. The **Mean**
    would not be affected in this case because of any extreme values as
    there are none.

-   Measure of Spread- Standard Deviation(SD)

    The Standard Deviation(SD) is a measurement of how much a group of
    values vary or are dispersed. While a high standard deviation
    suggests that the values are dispersed over a wider range, a low
    standard deviation suggests that the values tend to be close to the
    mean (also known as the anticipated value) of the collection.

```{r}
sd(amazon$discount_percentage)
```

-   Explanation for Choosing Standard Deviation(SD)- Standard Deviation
    is chosen here as it is calculated using all of the column's values,
    and it is given using the original units of measurement. It reveals
    the average (or standard) separation between each score and the
    distribution's mean.

    #### Visualization for 'discount_percentage' Variable with Mean & SD-

```{r}
# Mean and standard deviation
mean_value <- mean(amazon$discount_percentage)
sd_value <- sd(amazon$discount_percentage)

# Plot with mean and sd lines
ggplot(amazon, aes(x = discount_percentage)) +
  geom_histogram(alpha = 0.7, 
                 bins = 30, 
                 fill = "paleturquoise3", 
                 color = "darkslategray") +
  stat_function(fun = function(x) dnorm(x, 
                                        mean = mean_value, 
                                        sd = sd_value)*length(amazon$discount_percentage),
                aes(color = "Mean"), 
                size = 1.5) +
  stat_function(fun = function(x) dnorm(x, 
                                        mean = mean_value, 
                                        sd = sd_value)*length(amazon$discount_percentage) + mean_value,
                aes(color = "Mean + SD"), 
                size = 1.5) +
  stat_function(fun = function(x) dnorm(x, 
                                        mean = mean_value, 
                                        sd = sd_value)*length(amazon$discount_percentage) - mean_value,
                aes(color = "Mean - SD"), 
                size = 1.5) +
  labs(title = "BEHAVIOR OF DISCOUNT PERCENTAGE OF PRODUCTS", 
       x = "Percentage of Discount", 
       y = "Count") +
  theme_minimal(base_size = 16) +
  theme(plot.title = element_text(face = "bold",
                            hjust = 0.5,
                            color = "darkslategray"),
        axis.line = element_line(size = 1, 
                                 color = "darkslategray"),
        axis.text = element_text(color = "darkslategray"),
        axis.title = element_text(size = 16, 
                                  color = "darkslategray", 
                                  face="bold"),
        legend.position = "bottom",
        legend.title = element_text(size = 14, 
                                    color = "darkslategray", 
                                    face="bold"),
        legend.text = element_text(size = 12, 
                                   color = "darkslategray")) +
  scale_color_manual(values = c("Mean" = "red", 
                                "Mean + SD" = "blue", 
                                "Mean - SD" = "darkgreen")) 

```

## BIVARIATE ANALYSIS:

### 1. Numerical against Numerical

#### a. Visualization of 'mean_discounted_price' Against 'mean_actual_price'

```{r}
#plot 5
#point graph of mean actual price and mean discounted price
amazon_summary <- amazon %>%
group_by(main_category, rating) %>%
summarise(mean_actual_price = mean(actual_price),
mean_discounted_price = mean(discounted_price))
# remove grouping variable
ggplot(amazon_summary, aes(x = mean_actual_price, y = mean_discounted_price, color = rating)) +
geom_point(alpha = 0.7, size = 2) +
scale_x_log10() +
scale_y_log10() +
labs(title = "RELATIONSHIP BETWEEN THE MEAN OF ACTUAL PRICE & DISCOUNTED PRICE", x = "Mean Actual Price", 
     y = "Mean Discount Price", 
     color = "Rating") +
theme_bw() +
  theme(plot.title = element_text(face = "bold",
                            hjust = 0.5,
                            color = "hotpink4"),
        axis.line = element_line(color = "hotpink4"),
        axis.text = element_text(color = "hotpink4"),
        axis.title = element_text(size = 16, 
                                  color = "hotpink4", 
                                  face="bold"),
        legend.text = element_text(size = 12, 
                                   color = "hotpink4"),
        legend.title = element_text(size = 14, 
                                    color = "hotpink4", 
                                    face="bold"))
```

##### Analysis-

-   Relationship Between the Two Variables- The graph represents a
    scatter plot that shows the relationship between the 'mean actual
    price' and 'mean discounted price' of products sold on Amazon. Each
    point on the plot represents a combination of mean actual and mean
    discounted price for a specific rating category. The points are
    colored according to the rating category. The x-axis shows the mean
    actual price and the y-axis shows the mean discounted price.

```{r}
cor(amazon_summary$mean_actual_price, amazon_summary$mean_discounted_price, method = c("pearson", "kendall", "spearman"))
```

```{r}
cor.test(amazon_summary$mean_actual_price, amazon_summary$mean_discounted_price, method = c("pearson", "kendall", "spearman"))
```

-   Explanation for Correlation- The Correlation Coefficient can either
    be negative of positive. This also means that the relationship
    between the two variables can be negative or positive. Negative
    coefficient implies that when the value of one variable increases,
    the other decreases and moves in the opposite direction. Here, as
    the coefficient is positive, it means that as the value of mean
    actual price increases, the value of mean discounted price also goes
    up.

-   Form, Strength & Direction:

    The form of the observed relationship- It is positive and linear,
    indicating that as the mean actual price increases, the mean
    discounted price also tends to increase.

    The strength of the relationship- This relationship appears to be
    moderate to strong, as the points are tightly clustered around a
    linear trend-line and the correlation coefficient is positively
    close to 1.

    The direction of the relationship- The direction is positive, which
    means that the two variables move in the same direction.

-   Relationship in Context of the Data- The relationship between mean
    actual price and mean discounted price in the context of Amazon
    sales data suggests that higher-priced products tend to have higher
    discounted prices as well. This may be due to competitive pricing
    strategies, seasonal sales, or other factors. Additionally, the
    relationship between these two variables may be important for
    sellers to consider when pricing their products, as higher-priced
    products may need to be discounted more in order to remain
    competitive.

-   Variablity Observed in the Graph- The variability observed in the
    plot refers to the spread of the points around the trendline. In
    this plot, there appears to be moderate variability, as there are
    some points that deviate from the trendline. This variability
    corresponds to the strength of the observed relationship, as
    stronger relationships tend to have less variability or scatter
    around the trendline, while weaker relationships have more
    variability. In this case, the moderate variability indicates a
    moderate to strong relationship between the two variables.

#### b. Visualization of 'discount_percentage' Against 'rating'

Before plotting the graph for discount percentage and rating, we need to
check the datatype and the range of the variable so as to perform a log
transformation on the same to get a better visualization.

```{r}
# Check the data type and range of the variable you're trying to log transform
class(amazon$discount_percentage)
range(amazon$discount_percentage)

# Convert the variable to numeric if it's a factor or character
amazon$discount_percentage <- as.numeric(as.character(amazon$discount_percentage))

# Adjust the range of the data or use a different transformation if the variable contains negative values
amazon$discount_percentage <- amazon$discount_percentage + abs(min(amazon$discount_percentage)) + 1

str(amazon$actual_price)
str(amazon$discount_price)

amazon$actual_price <- as.numeric(amazon$actual_price)
amazon$discounted_price <- as.numeric(amazon$discounted_price)
```

```{r}
#plot 6
#hex plot of rating and discount percentage
ggplot(amazon, aes(x=rating,y=discount_percentage)) +
  geom_hex(bins=25) +
  labs(x="Rating", y="Discount Percentage", title="RELATIONSHIP BETWEEN DISCOUNT PERCENTAGE & RATING") +
  scale_fill_continuous(name="Frequency") +
  theme_minimal(base_size = 16) +
  theme(plot.title = element_text(face = "bold",
                            hjust = 0.5,
                            color = "midnightblue"),
    axis.line = element_line(color = "midnightblue"),
        axis.text = element_text(size = 12, 
                                 color = "midnightblue"),
        axis.title = element_text(size = 12, 
                                  color = "midnightblue", 
                                  face="bold"),
        legend.position = "right",
        legend.title = element_text(size = 12, 
                                    color = "midnightblue", 
                                    face="bold"),
        legend.text = element_text(size = 12, 
                                   color = "midnightblue")) +
  guides(fill = guide_colorbar(title.position = "top"))
```

-   Relationship between the Two Variables- The given plot is an
    appropriate plot to visualize the relationship between the two
    variables rating and discount_percentage. It is a hexagonal bin plot
    with 25 bins, which shows the distribution of the data points in the
    plot.

```{r}
cor(amazon$net, amazon$discount_percentage, method = c("pearson", "kendall", "spearman"))
```

```{r}
cor.test(amazon$net, amazon$discount_percentage, method = c("pearson", "kendall", "spearman"))
```

-   Explanation for Correlation- The plot shows a negative relationship
    between the two variables, i.e., as rating increases,
    discount_percentage decreases. The Correlation Coefficient being
    negative tells us that the two variables are negatively related;
    meaning that when the value of one increases, the value of the other
    decreases.

-   Form, Direction & Strength:

    Form of the Relationship- It is a non-linear type of association as
    when the value of one rises up the other one falls down.

    Direction of the Relationship- The direction is negative as these
    two variables are inversely related to each other. This is evident
    from the correlation test because when the bar for one rises up the
    other degrades and falls down.

    The strength of the Relationship- The strength is moderate, as we
    can see a general trend of decreasing discount_percentage as rating
    increases, but there is also a lot of variability in the plot.

-   Relationship in Context of the Data- The negative relationship
    between rating and discount percentage means that products with
    higher ratings tend to have lower discounts, while products with
    lower ratings tend to have higher discounts. This may indicate that
    highly-rated products are in high demand and therefore do not
    require steep discounts to sell, while lower-rated products need
    more incentives such as discounts to sell.

-   Variability Observed in the Graph- The plot shows a lot of
    variability in the distribution of the data points, which
    corresponds to the moderate to mild strength of the observed
    relationship and it is also supported by the correlation coefficient
    calculated. We can see some areas of the plot with high frequency of
    data points, indicating a stronger relationship in those areas, but
    there are also many areas with low frequency, indicating a weaker
    relationship in those areas. Overall, the plot shows a general trend
    but also a lot of variability, which corresponds to the moderate
    strength of the observed relationship.

### 2. Categorical against Numerical

#### a. Visualization of 'discount_percentage' Against 'main_category'

```{r}
#plot 7
ggplot(amazon, aes(x = main_category, 
                   y = discount_percentage, 
                   fill = main_category)) +
  geom_boxplot(alpha = 0.7) +
  labs(x = "Product Category", y = "Discount Percentage", fill = "Product Category",
       title = "DISCOUNT PERCENTAGE FOR PRODUCT CATEGORIES") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, color = "black", size = 12),
        axis.text.y = element_text(color = "black"),
        axis.title = element_text(color = "black", 
                                  size = 14, 
                                  face = "bold"),
        legend.position = "bottom",
        legend.title = element_text(color = "black", 
                                    size = 12, 
                                    face = "bold"),
        legend.text = element_text(color = "black", 
                                   size = 12),
        panel.grid.major = element_line(color = "gray", 
                                        linetype = "dashed"),
        panel.background = element_rect(fill = "white"),
        plot.title = element_text(face = "bold", 
                                  size = 16, 
                                  color = "black"))
```

-   Relationship between the Two Variables- The code creates a boxplot
    to visualize the distribution of discount percentage across
    different product categories. Each box represents a product
    category, and the height of the box indicates the interquartile
    range (IQR) of the discount percentage within that category. The
    horizontal line within the box indicates the median value of the
    discount percentage, and the whiskers extending from the box
    represent the range of the discount percentage within 1.5 times the
    IQR. Any points outside of the whiskers are considered outliers.

-   Form, Direction & Strength-

    The form of the relationship is that the distribution of discount
    percentage varies across different product categories.

    The direction of the relationship is not applicable as we are not
    comparing two continuous variables.

    The strength of the relationship is moderate, as there is noticeable
    variation in the distribution of discount percentage across the
    different product categories.

-   Relationship with respect to the Context of Dataset- This
    relationship means that different product categories have different
    levels of discount percentages. For example, the "Sports and
    Outdoors" category generally has higher discount percentages than
    the "Home and Kitchen" category. This could be due to a number of
    factors, such as the competitive landscape within each category, the
    seasonality of products within each category, or the perceived value
    of products within each category.

-   Variability Observed- The variability in the plot is moderate, as
    there is noticeable variation in the distribution of discount
    percentage across the different product categories. This variability
    corresponds to the moderate strength of the relationship that was
    calculated in , as there is not a clear trend or pattern in the
    distribution of discount percentage across the product categories,
    but there is still noticeable variation that suggests there may be
    some underlying factors that are influencing the discount
    percentages within each category.

#### b. Visualization of 'net' Against 'status'

```{r}
#plot 8
#bar plot of net sales and status
ggplot(amazon, aes(x = status, y = net, fill = main_category)) +
  geom_col() + 
  scale_fill_brewer(palette = "Spectral") +
  coord_flip() +
  labs(x = "Status", y = "Net Sales", fill = "Product Category",
       title = "RATING CLASSIFICATION") +
  theme_bw() +
  theme(axis.text.x = element_text(size = 12, 
                                   color = "red4"),
        axis.text.y = element_text(size = 12, 
                                   color = "red4"),
        axis.title = element_text(size = 14, 
                                  color = "red4", 
                                  face = "bold"),
        legend.position = "right",
        legend.title = element_text(size = 12, 
                                    color = "red4", 
                                    face = "bold"),
        legend.text = element_text(size = 12, 
                                   color = "red4"),
        panel.grid.major = element_line(color = "gray", 
                                        linetype = "dashed"),
        panel.background = element_rect(fill = "white"),
        plot.title = element_text(size = 16, 
                                  color = "red4", 
                                  face = "bold"))

```

-   Relationship between the Two Variables- We can clearly interpret
    from the graph that each bar of the status of the rating have their
    unique number of observations in the rating section. The 'bad'
    status is obtained from least number of ratings that have been got,
    while the 'excellent' status has be obtained from most number of
    ratings. 'good' status has been interpreted from a moderate number
    of ratings observed. Thus we see that the relationship between these
    two variables is strong.

-   Form, Direction & Strength-

    The relationship takes the shape that ratings are distributed
    differently across various rating statuses.

    Since we are not comparing two continuous variables, the direction
    of the link is irrelevant.

    Given the apparent fluctuation in the distribution of ratings among
    the various rating statuses, the link is clearly strong.

-   Relationship with respect to the Context of Dataset- As a result of
    this relationship, different rating statuses provide various amounts
    of ratings. This could be caused by a variety of things, including
    the level of competition in each category, the seasonality of the
    products, or the perceived worth of the goods in each category.

-   Variability Observed- Because the distribution of the rating among
    the various rating status varies noticeably, the plot's fluctuation
    is strong. As there is a discernible trend or pattern in the
    distribution of rating across the rating status, this variability
    corresponds to the atrong strength of the relationship that was
    calculated in. There may be some underlying factors that are
    influencing the rating within each rating status category.

## *References-*

*We have taken help from the following websites-*

1.  <https://universeofdatascience.com/>

2.  <https://www.marsja.se/>

3.  <http://www.stat.columbia.edu/~tzheng/files/Rcolor.pdf>

4.  <http://rstudio-pubs-static.s3.amazonaws.com/5312_98fc1aba2d5740dd849a5ab797cc2c8d.html>
